Supporting Information for Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-09-27 si.tex
more edits
still need to discuss (a) Kundu 2022 integrals, (b) impact of \Delta on spectra, and (c) impact of sign of M, dM/dQ etc on spectra.

For an $n$-quantum excited state vibration $| \tilde{n} \rangle$, and a $m$-quantum ground state vibration $\ket{m}$, the $k^{th}$-order vibrational coupling term is
\begin{equation}
	\begin{split}
		\mel{\tilde{n}}{q^k}{m} &= \int_{-\infty}^\infty \mathrm{d}q \ \psi^*_n(q-\Delta) q^k \psi_m(q)\\
		&= \int_{-\infty}^\infty \mathrm{d}q \ N_n H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k N_m H_m(q) \exp(-\frac{q^2}{2}). \\
		&= N_n N_m \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ H_n(q-\Delta) q^k H_m(q) \exp(-q^2 + q\Delta)
	\end{split}\label{key}
\end{equation}
The integral corresponds to Franck-Condon factors for $k=0$ and Herzberg-Teller matrix elements for $k=1$.

\subsection{General Solution to $\langle \tilde{n} | q^k | m \rangle$}
The matrix elements of \autoref{key} can be computed numerically, but analytic forms of the integral also exist. 
Due to the polynomial nature of $H_v(q)$, the product $H_n(q-\Delta) q^k H_m(q)$ will also be a polynomial, so that the integral of equation \autoref{key} will be of the form
\begin{eqnarray}
	\int_{-\infty}^\infty \mathrm{d}q \ P_{nmk}(q) \exp(-q^2 + q\Delta), \\
	P_{nmk}(q) \equiv \sum_\lambda^{n+m+k} a_\lambda q^\lambda
\end{eqnarray}
for some set coefficients $a_\lambda$, to be specified later. We can recast the integral into the linear combination of integrals,
\begin{equation}\label{eq:analytic_form}
	\mel{\tilde{n}}{q^k}{m} = N_n N_m \exp(-\frac{\Delta^2}{2}) \sum_\lambda a_\lambda F_\lambda(\Delta),
\end{equation}
where
\begin{equation}\label{integral}
	F_w(\Delta) \equiv \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta).
\end{equation}
\autoref{integral} can be readily evaluated, as we now show.  When $w=0$, the integral is evaluated by completing the square:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
\begin{equation}
	\begin{split}
		F_0(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 - q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
		&= \exp(\frac{\Delta^2}{4}) \int_{-\infty}^\infty \mathrm{d}q \exp(-(q - \frac{\Delta}{2})^2) \\
		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
	\end{split}
\end{equation}
For the general solution, \autoref{integral} is evaluated via repeated use of a well-known Gaussian identity
\begin{equation}\label{identity}
	\begin{split}
		F_w(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta) = \partial_{\Delta} \int_{-\infty}^\infty \mathrm{d}q \ q^{w-1} \exp(-q^2 + q\Delta) \\
		&= \partial_\Delta F_{w-1}(\Delta)
	\end{split}
\end{equation}
so we can write\footnote{Setting $-x^2 \ = \ \Delta^2/4$ (so that $x \ = \ i \Delta /2$) and using the chain rule ($\mathrm{d}/\mathrm{d}x = \mathrm{d}/\mathrm{d}\Delta \ \mathrm{d}\Delta / \mathrm{d}x$) provides the final result in \autoref{eq:F_solved}}
\begin{equation}\label{eq:F_solved}
	\begin{split}
		F_w(\Delta) &= \left(\partial_\Delta \right)^w F_0(\Delta) \\
		&= \sqrt{\pi} \frac{\mathrm{d}^w}{\mathrm{d}\Delta^w} \exp(\frac{\Delta^2}{4}) \\
		&= \sqrt{\pi} \left( -\frac{i}{2} \right)^w \exp(\frac{\Delta^2}{4}) H_w\left(i\frac{\Delta}{2}\right).
	\end{split}
\end{equation}
In the last line we have used the generator definition of Hermite polynomials:  $H_n(x) \equiv (-1)^n e^{x^2} \frac{\mathrm{d}^n}{\mathrm{d}x^n} e^{-x^2}$.

We now will evaluate the polynomial coefficients $P(q)$.
The Hermite polynomials of \autoref{key} can be explicitly written as 
\begin{equation}
\begin{split}
	H_m(q) &= \sum_{s=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2s)} q^{m-2s} \\
	H_n(q-\Delta) &= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor}
	a_n^{(n-2s)} (q-\Delta)^{n-2s} \\
		&= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2s)} \sum_{l=0}^{n-2s} \left(-\Delta\right)^{n-2s-l} \binom{n-2s}{l} q^l
\end{split}
\end{equation}
where $\left\lfloor n \right\rfloor$ denotes the \textit{floor} of $n$, $\binom{a}{b} = a! / (b!(a-b)!)$, and the Hermite coefficients are\cite{MorseFeshbach}
\begin{equation}
	a_n^{(n-2s)} = n! \frac{(-1)^x 2^{n-2s}}{s!(n-2s)!}.
\end{equation}
Multiplying these terms together give us explicit polynomial coefficients:
\begin{equation}\label{eq:poly_solved}
\begin{split}
	P_{nmk}(q) %&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2x)} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2y)} \sum_{l=0}^{n-2y} \Delta^{n-2y-l} \binom{n-2y}{l} q^{l+m-2x+k} \\
	&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} c_{xyl} \ q^{l+m-2x+k}, \\
	c_{xyl} &= a_m^{(m-2x)} a_n^{(n-2y)} \left(-\Delta\right)^{n-2y-l} \binom{n-2y}{l}.
\end{split}
\end{equation}
\autoref{eq:poly_solved} is not in standard polynomial form, because our summation is not singular and coefficients in our summation may have the same power. 
Further simplifications can be made to sum to reduce recounting indices, but we do not find these simplifications essential.
Regardless, substituting \autoref{eq:F_solved} and \autoref{eq:poly_solved} into \autoref{eq:analytic_form}, we can now evaluate the solution as:
\begin{equation}\label{eq:general_solution}
	\mel{\tilde{n}}{q^k}{m} = \sqrt{\pi} N_n N_m 
	\exp(-\frac{\Delta^2}{4}) \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+m-2x+k} c_{xyl} H_{l+m-2x+k}\left(i\frac{\Delta}{2}\right).
\end{equation}
An alternative approach has been introduced by Kundu \textit{et al}, which yields effectively identical results. \cite{Kundu2022}

\subsection{Evaluating Herzberg Teller terms for HDFG}
When starting from $\ket{0}$,
\begin{equation}
\begin{split}
	\langle \tilde{n} |q| 0 \rangle &= 
	\sqrt{\pi} N_n N_0 \exp(-\frac{\Delta^2}{4}) \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+1} c_{0yl} H_{l+1}\left(i\frac{\Delta}{2}\right) \\
	&= \sqrt{n! \ 2^n} \exp(-\frac{\Delta^2}{4})
	\sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} 
	\frac{(-1)^y}{2^{2y}y!}
	\sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+1} 
	\frac{\left(-\Delta\right)^{n-2y-l}}{l!(n-2y-l)!}
	H_{l+1}\left(i\frac{\Delta}{2}\right)
\end{split}
\end{equation}
giving the first few relevant integrals as
\begin{equation}
	\langle \tilde{0} |q| 0 \rangle = \frac{\Delta}{2} \exp(-\frac{\Delta^2}{4})
\end{equation}

@@

Similarly, when starting from $\ket{1}$, 
\begin{equation}
	\begin{split}
		\langle \tilde{n} |q| 1 \rangle &= \sqrt{\pi} N_n N_1 \exp(-\frac{\Delta^2}{4}) \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+2} c_{1yl} H_{l+2}\left(i\frac{\Delta}{2}\right) \\
		&= 
		\sqrt{n! \ 2^{n+1}} \exp(-\frac{\Delta^2}{4}) 
		\sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} 
		\frac{(-1)^y}{2^{2y}y!}
		\sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+2} 
		\frac{\left(-\Delta\right)^{n-2y-l}}{l!(n-2y-l)!}
		H_{l+2}\left(i\frac{\Delta}{2}\right)
	\end{split}
\end{equation}
giving
\begin{equation}
	\langle \tilde{0} |q| 1 \rangle = \frac{\sqrt{2}}{4}\left( \Delta^2 + 2 \right)
	\exp(-\frac{\Delta^2}{4})
\end{equation}
\begin{equation}
	\langle \tilde{1} |q| 1 \rangle = \frac{\sqrt{2}}{4}\left( -\Delta^3 + 2\Delta \right)
	\exp(-\frac{\Delta^2}{4})
\end{equation}
\begin{equation}
	\langle \tilde{2} |q| 1 \rangle = \frac{1}{8} \left( \Delta^4 - 6\Delta^2 + 8 \right)
	\exp(-\frac{\Delta^2}{4})
\end{equation}

These integrals, along with some relevant Franck-Condon factors, are plotted below as a function of offset.

@@

\newpage
\section{Impact of displacement, resonance frequencies, vibronic linewidth and molecular parameters on HDFG Spectra}
Inspection of the $A,B$ terms in the main text show that the HDFG output is dependent upon the relative size of products of Franck-Condon and Herzberg-Teller integrals.
For clarity, we plot the relevant product factors to assist in understanding the impact of offset on the HDFG spectra.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/fcht_product.png}
	\caption{Products of Franck-Condon and Herzberg-Teller integrals relevant to the $A, B_1, B_2$ terms in this manuscript as a function of offset, $\Delta$.} 
	\label{fig:fcht_product}
\end{figure}

These plots highlight the important distinction that $B$ term contributions to HDFG can dominate in the limit of small offset.
This is expected, as when $\Delta \rightarrow 0$, the overlap integral \autoref{key} resolves into the typical harmonic oscillator selection rules.

@@

In the main text, the potential well offset ($\Delta$) was taken as $\Delta = 0.5$.
Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.
The dependence of relevant Franck-Condon factors and Herzberg-Teller factors on displacement are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
\autoref{fig:fcht} shows how different displacements, vibrational frequencies, and vibronic linewidths will alter the vibronic spectrum.

It is clear from \autoref{fig:fcht} that the HDFG spectrum will have a significant dependence upon $\Delta$, even for small deviations from complete overlap. 
To this end, we plot the impact of resonance frequency and offset on the HDFG spectrum \autoref{fig:chgdelta}, using values reported by Myers et al. and Brennan et al. \cite{Myers1982, Brennan2024}
In this section, we take $\omega_{eg}$ = $37340$ cm$^{-1}$ and vary the offset ($\Delta$), vibrational frequency ($\omega_{g1,g0}$), and linewidth ($\Gamma$) as noted in the figure.

>>>>

For an $n$-quantum excited state vibration $| \tilde{n} \rangle$, and a $m$-quantum ground state vibration $\ket{m}$, the $k^{th}$-order vibrational coupling term is
\begin{equation}
	\begin{split}
		\mel{\tilde{n}}{q^k}{m} &= \int_{-\infty}^\infty \mathrm{d}q \ \psi^*_n(q-\Delta) q^k \psi_m(q)\\
		&= \int_{-\infty}^\infty \mathrm{d}q \ N_n H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k N_m H_m(q) \exp(-\frac{q^2}{2}). \\
		&= N_n N_m \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ H_n(q-\Delta) q^k H_m(q) \exp(-q^2 + q\Delta)
	\end{split}\label{key}
\end{equation}
The integral corresponds to Franck-Condon factors for $k=0$ and Herzberg-Teller matrix elements for $k=1$.
The vibrational coupling integrals are written assuming the expansion of the dipole moment is taken about the equilibirum point of the ground state geometry ($q=0$), as is done in the main text.

\subsection{General Solution to $\langle \tilde{n} | q^k | m \rangle$}
The matrix elements of \autoref{key} can be computed numerically, but analytic forms of the integral also exist. 
Due to the polynomial nature of $H_v(q)$, the product $H_n(q-\Delta) q^k H_m(q)$ will also be a polynomial, so that the integral of equation \autoref{key} will be of the form
\begin{eqnarray}
	\int_{-\infty}^\infty \mathrm{d}q \ P_{nmk}(q) \exp(-q^2 + q\Delta), \\
	P_{nmk}(q) \equiv \sum_\lambda^{n+m+k} a_\lambda q^\lambda
\end{eqnarray}
for some set coefficients $a_\lambda$, to be specified later. We can recast the integral into the linear combination of integrals,
\begin{equation}\label{eq:analytic_form}
	\mel{\tilde{n}}{q^k}{m} = N_n N_m \exp(-\frac{\Delta^2}{2}) \sum_\lambda a_\lambda F_\lambda(\Delta),
\end{equation}
where
\begin{equation}\label{integral}
	F_w(\Delta) \equiv \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta).
\end{equation}
\autoref{integral} can be readily evaluated, as we now show.  When $w=0$, the integral is evaluated by completing the square:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
\begin{equation}
	\begin{split}
		F_0(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 - q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
		&= \exp(\frac{\Delta^2}{4}) \int_{-\infty}^\infty \mathrm{d}q \exp(-(q - \frac{\Delta}{2})^2) \\
		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
	\end{split}
\end{equation}
For the general solution, \autoref{integral} is evaluated via repeated use of a well-known Gaussian identity
\begin{equation}\label{identity}
	\begin{split}
		F_w(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta) = \partial_{\Delta} \int_{-\infty}^\infty \mathrm{d}q \ q^{w-1} \exp(-q^2 + q\Delta) \\
		&= \frac{\mathrm{d}}{\mathrm{d}\Delta} F_{w-1}(\Delta)
	\end{split}
\end{equation}
so we can write\footnote{Setting $-x^2 \ = \ \Delta^2/4$ (so that $x \ = \ i \Delta /2$) and using the chain rule ($\frac{\mathrm{d}}{\mathrm{d}x} =  \frac{\mathrm{d}}{\mathrm{d}\Delta}  \frac{\mathrm{d\Delta}}{\mathrm{d}x}$) provides the final result in \autoref{eq:F_solved}.}
\begin{equation}\label{eq:F_solved}
	\begin{split}
		F_w(\Delta) &= \frac{\mathrm{d}^w}{\mathrm{d}\Delta^w} F_0(\Delta) \\
		&= \sqrt{\pi} \frac{\mathrm{d}^w}{\mathrm{d}\Delta^w} \exp(\frac{\Delta^2}{4}) \\
		&= \sqrt{\pi} \left( -\frac{i}{2} \right)^w \exp(\frac{\Delta^2}{4}) H_w\left(i\frac{\Delta}{2}\right).
	\end{split}
\end{equation}
In the last line we have used the generator definition of Hermite polynomials:  $H_n(x) \equiv (-1)^n e^{x^2} \frac{\mathrm{d}^n}{\mathrm{d}x^n} e^{-x^2}$.\cite{MorseFeshbach}

We now will evaluate the polynomial coefficients $P(q)$.
The Hermite polynomials of \autoref{key} can be explicitly written as 
\begin{equation}
\begin{split}
	H_m(q) &= \sum_{s=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2s)} q^{m-2s} \\
	H_n(q-\Delta) &= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor}
	a_n^{(n-2s)} (q-\Delta)^{n-2s} \\
		&= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2s)} \sum_{l=0}^{n-2s} \left(-\Delta\right)^{n-2s-l} \binom{n-2s}{l} q^l
\end{split}
\end{equation}
where $\left\lfloor n \right\rfloor$ denotes the \textit{floor} of $n$, $\binom{a}{b} = a! / (b!(a-b)!)$, and the Hermite coefficients are\cite{MorseFeshbach}
\begin{equation}
	a_n^{(n-2s)} = n! \frac{(-1)^x 2^{n-2s}}{s!(n-2s)!}.
\end{equation}
Multiplying these terms together give us explicit polynomial coefficients:
\begin{equation}\label{eq:poly_solved}
\begin{split}
	P_{nmk}(q) %&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2x)} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2y)} \sum_{l=0}^{n-2y} \Delta^{n-2y-l} \binom{n-2y}{l} q^{l+m-2x+k} \\
	&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} c_{xyl} \ q^{l+m-2x+k}, \\
	c_{xyl} &= a_m^{(m-2x)} a_n^{(n-2y)} \left(-\Delta\right)^{n-2y-l} \binom{n-2y}{l}.
\end{split}
\end{equation}
\autoref{eq:poly_solved} is not in standard polynomial form, because the summation is not singular and coefficients in the summation may have the same power. 
Further simplifications can be made to reduce recounting indices, but we do not find these simplifications essential.
Regardless, substituting \autoref{eq:F_solved} and \autoref{eq:poly_solved} into \autoref{eq:analytic_form}, we can now evaluate the solution as:
\begin{equation}\label{eq:general_solution}
	\mel{\tilde{n}}{q^k}{m} = \sqrt{\pi} N_n N_m 
	\exp(-\frac{\Delta^2}{4}) \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+m-2x+k} c_{xyl} H_{l+m-2x+k}\left(i\frac{\Delta}{2}\right).
\end{equation}

\subsection{Evaluating Herzberg Teller terms for HDFG}
When evaluating Herzberg-Teller integrals involving $\ket{0}$,
\begin{equation}
\begin{split}
	\langle \tilde{n} |q| 0 \rangle &= 
	\sqrt{\pi} N_n N_0 \exp(-\frac{\Delta^2}{4}) \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+1} c_{0yl} H_{l+1}\left(i\frac{\Delta}{2}\right) \\
	&= \sqrt{n! \ 2^n} \exp(-\frac{\Delta^2}{4})
	\sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} 
	\frac{(-1)^y}{2^{2y}y!}
	\sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+1} 
	\frac{\left(-\Delta\right)^{n-2y-l}}{l!(n-2y-l)!}
	H_{l+1}\left(i\frac{\Delta}{2}\right)
\end{split}
\end{equation}
giving the first few relevant integrals as
\begin{equation}
	\langle \tilde{0} |q| 0 \rangle = \frac{\Delta}{2} \exp(-\frac{\Delta^2}{4})
\end{equation}

@@

Similarly, when evaluating Herzberg-Teller integrals involving $\ket{1}$, 
\begin{equation}
	\begin{split}
		\langle \tilde{n} |q| 1 \rangle &= \sqrt{\pi} N_n N_1 \exp(-\frac{\Delta^2}{4}) \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+2} c_{1yl} H_{l+2}\left(i\frac{\Delta}{2}\right) \\
		&= 
		\sqrt{n! \ 2^{n+1}} \exp(-\frac{\Delta^2}{4}) 
		\sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} 
		\frac{(-1)^y}{2^{2y}y!}
		\sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+2} 
		\frac{\left(-\Delta\right)^{n-2y-l}}{l!(n-2y-l)!}
		H_{l+2}\left(i\frac{\Delta}{2}\right)
	\end{split}
\end{equation}
giving
\begin{equation}
	\langle \tilde{0} |q| 1 \rangle = \frac{\sqrt{2}}{4}\left( \Delta^2 + 2 \right)
	\exp(-\frac{\Delta^2}{4})
\end{equation}
\begin{equation}
	\langle \tilde{1} |q| 1 \rangle = \frac{\sqrt{2}}{4}\left( -\Delta^3 + 2\Delta \right)
	\exp(-\frac{\Delta^2}{4})
\end{equation}
\begin{equation}
	\langle \tilde{2} |q| 1 \rangle = \frac{1}{8} \left( \Delta^4 - 6\Delta^2 + 8 \right)
	\exp(-\frac{\Delta^2}{4})
\end{equation}

These integrals, along with some relevant Franck-Condon factors, are plotted in \autoref{fig:fcht} as a function of offset.

@@

\newpage
\section{Impact of displacement, resonance frequencies, vibronic linewidth and molecular parameters on HDFG Spectra}
Inspection of the $A,B$ terms in the main text show that the HDFG output is dependent upon the relative size of products of Franck-Condon and Herzberg-Teller integrals.
For clarity, we plot the relevant product factors to assist in understanding the impact of offset on the HDFG spectra (\autoref{fig:fcht_product}).
These plots highlight the important distinction that $B$ term contributions to HDFG can dominate in the limit of small offset.
This is expected, as when $\Delta \rightarrow 0$, the overlap integral, \autoref{key}, returns typical harmonic oscillator selection rules.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/fchtproduct.png}
	\caption{Products of Franck-Condon and Herzberg-Teller integrals relevant to the $A, B_1, B_2$ terms in this manuscript as a function of offset, $\Delta$.} 
	\label{fig:fcht_product}
\end{figure}

In the main text, the potential well offset ($\Delta$) was taken as $\Delta = 0.5$.
Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.
The dependence of relevant Franck-Condon factors and Herzberg-Teller factors on displacement are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
\autoref{fig:fcht} shows how different displacements, vibrational frequencies, and vibronic linewidths will alter the vibronic spectrum.
The products of Franck-Condon and Herzberg-Teller integrals relevant to the $A,B$ coefficents discussed in the main text are plotted in \autoref{fig:fcht_product}.

It is clear from \autoref{fig:fcht_product} that the HDFG spectrum will have a significant dependence upon $\Delta$, even for small deviations from complete overlap. 
To this end, we plot the impact of resonance frequency and offset on the HDFG spectrum \autoref{fig:chgdelta}, using values reported by Myers et al. and Brennan et al. \cite{Myers1982, Brennan2024}
In this section, we take $\omega_{eg}$ = $37340$ cm$^{-1}$ and vary the offset ($\Delta$), vibrational frequency ($\omega_{g1,g0}$), and linewidth ($\Gamma$) as noted in the figure.

@@

%todo: plot impact of different A,B on output.
